Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Logical headings.
Removing empty lines at end of document.
Starting report on p. 2.
Captions comment.
Numbered lines.

# Introduction

@@

### Phase 1: How to harvest and analyze the data? {.smaller}

@@

@@

### Phase 2: Exploring solutions {.smaller}

@@

### Phase 3: Scrapping the scraping {.smaller}

@@

During the case we realized that we had to limit our solution. The case 
presented by OPX wanted an automated code which would retrieve the data 
and calculate the different KPIs, which turned out not to be possible. 
The limitations can be divided into problems regarding: 
(i) the accessible data, and 
(ii) the non-accessible data

>>>>

<!--# Starting report on second page to avoid a tiny text portion below the toc-->
\newpage
# Introduction

@@

## Phase 1: How to harvest and analyze the data? {.smaller}

@@

<!-- # All images need captions-->

@@

## Phase 2: Exploring solutions {.smaller}

@@

## Phase 3: Scrapping the scraping {.smaller}

@@

During the case we realized that we had to limit our solution. The case 
presented by OPX wanted an automated code which would retrieve the data 
and calculate the different KPIs, which turned out not to be possible. 
The limitations can be divided into problems regarding:

1. the accessible data, and 
2. the non-accessible data
